## Reproducible Research: Peer Assessment 1


This assignment is broken into 5 parts, each part will deal with different
aspects of reproducible research.


### Loading and preprocessing the data

To load in the csv file I used the `read.csv()` function. I then used the 
`transform()` function to convert the date field from a factor to a date type.

```{r}
activity <- read.csv(file="activity.csv")
activity <- transform(activity, date = as.Date(date))
```

### What is mean total number of steps taken per day?

Once the data is in the correct format I can now create some exploratory graphs
using the `ggplot()` function in the `ggplot2` package. This needs to be loaded 
into R using the `library()` function.

```{r}
library(ggplot2)
aggData <- aggregate(steps ~ date, data=activity, FUN=sum)
ggplot(aggData, aes(steps)) + geom_histogram(binwidth=600)
```

The mean and median can be calculated using the `aggData` variable we created 
and the `mean()` and `median()` functions as follows;

```{r}
meanSteps <- mean(aggData$steps)
meanSteps
medianSteps <- median(aggData$steps)
medianSteps
```

### What is the average daily activity pattern?
```{r}
aggDataInterval <- aggregate(steps ~ interval, data=activity, FUN=mean)
ggplot(aggDataInterval, aes(interval,steps)) + geom_line() + 
        xlab("5 minute interval") + ylab("Average number of steps")
```

The 5-minute interval with the highest average number of steps can be found
using the `which.max()` function and indexing into the aggregate data frame;

```{r}
aggDataInterval[which.max(aggDataInterval$steps), ]
```

### Imputing missing values



### Are there differences in activity patterns between weekdays and weekends?
